SDR enhancement by clouds

### 2024-03-13 article/article.Rmd
Commit 2024-03-13 17:10

@@

Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that atternuate the GHI, execluding clouds.

>>>>

Our monitoring site is operated by the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ()

@@

Which is an expected result as these values represent an typical atmosphere in Thessaloniki with low load of aerosols and humidity, which are the main factor that attenuate the GHI, excluding clouds.
